### 2024-11-29 paper/intro.tex
Fix intro

% Challenge
One challenge of our approach is making AL executable.
Since the prose specification is written in informal pseudocode, its
interpretation is not straightforward.
The naive implementation of AL interpreter produced incorrect results when
running Wasm official test suites, particularly those related to control flow.
Additionally, the absence of a formalized definition or formal semantics for AL
made it difficult to identify and address the fundamental issues in its design.
Since running tests is the primary method for assessing the correctness of the
specification, this limitation hindered the development of both the generated
interpreter and the specification itself.
This underscored the need for a more robust approach to formally define AL and
ensure its alignment with Wasm's complex semantics.

% Solution
To address this, we present a formal model for how the prose specification
describes Wasm semantics.
Using this model, we identify the underlying issues and the necessary changes
to improve it.
Based on these insight, we formally define AL's syntax and semantics to
accurately capture Wasm semantics.
We then implement an AL interpreter according to the formal definition and
evaluate its correctness.
The interpreter successfully passes all tests in the Wasm official test suite,
as well as tests from proposals.

>>>>

% 느낌 대신 "논리"적인 흐름에 집중 (일관성과 일맥상통)
% Challenge
When desiging the SpecTec, one of the challenges in our approach is making AL
executable.
In this master thesis, we focus on this specific challenge.
Since the prose specification is written in informal pseudocode, its
interpretation is not straightforward.
The absence of a formalized definition or formal semantics for the prose
specification posed significant difficulty in realizing executable AL.
Since executing the specification against tests is the primary method for
assessing its correctness, this limitation hindered the development of both the
generated interpreter and the specification itself.

% Solution
To address this, we present a formal model for how the prose specification
describes Wasm semantics.
Based on these insight, we formally define AL's syntax and semantics to
accurately capture Wasm semantics.
We then implement an AL interpreter according to the formal definition and
evaluate its correctness.
The interpreter successfully passes all tests in the Wasm official test suite,
as well as tests from proposals.
